### 2023-07-11 thesis/sections/3-exp-setup.tex
git friendly latex

This research investigates how agents communicate about the relations of objects seen in images. For that reason the original CLEVR dataset offers too little control over how the objects are created and in which relation they stand to each other. Following, I extended the source code to generated images for the CLEVR dataset.\footnote{The extended source code can be found on GitHub: \href{https://github.com/DominikKuenkele/MLT\_Master-Thesis\_clevr-dataset-gen}{https://github.com/DominikKuenkele/MLT\_Master-Thesis\_clevr-dataset-gen}} To simplify the generation, I only focused on the attributes \emph{shape}, \emph{size} and \emph{color}. The \emph{material} is always the same for all objects in a generated image. There were three main extensions to the code:

>>>>

This research investigates how agents communicate about the relations of objects seen in images.
For that reason the original CLEVR dataset offers too little control over how the objects are created and in which relation they stand to each other.
Following, I extended the source code to generated images for the CLEVR dataset.\footnote{\href{https://github.com/DominikKuenkele/MLT\_Master-Thesis\_clevr-dataset-gen}{https://github.com/DominikKuenkele/MLT\_Master-Thesis\_clevr-dataset-gen}}
To simplify the generation, I only focused on the attributes \emph{shape}, \emph{size} and \emph{color}.
The \emph{material} is always the same for all objects in a generated image.
There were three main extensions to the code:
